Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

This section supplies the proofs postponed from Section~\ref{sec:hv:type1}. We will start by presenting two properties underneath the procedures designed in Section~\ref{sec:hv:type1}. These properties will enable us to construct simpler proofs later.

@@

We now proceed to elaborate the proofs deferred from Section~\ref{sec:hv:type1}. The order of the subsequent proofs will not strictly follow the sequence in which they are referenced in Section~\ref{sec:hv:type1}. In particular, we will prove Lemma~\ref{lmm:hv:type1:properties} before Lemma~\ref{lmm:hv:type1:recur-output}, because the claims of the former lemma can be used to produce a succinct argument for the latter.

@@

\extraspacing \underline{\em Proof of Statement (1).} Let $\bm{t}$, $h$, and $v$ be as defined in the statement. 
Recall that $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$. Hence, the segments $h$ and $v$ both cross $B_\bm{t}$, as can be verified from the definitions of $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$. Thus, $h \cap v$ is a point $p$ in $B_\bm{t} = \bigcap_{i=1}^{k-2} \bm{t}[i]$. As $r_i$ ($i \in [k-2]$) is the full rectangle of $\bm{t}[i]$, we know that $\bigcap_{i=1}^{k-2} r_i$ covers $B_\bm{t} = \bigcap_{i=1}^{k-2} \bm{t}[i]$. Hence, point $p$ falls in $\bigcap_{i=1}^{k-2} r_i$, indicating that $h\cap v \cap \bigcap_{i = 1}^{k-2}r_i \neq \emptyset$. It follows that $(r_1,...,r_{k-2},h,v)$ is a result tuple in $\J(R_1,...,R_{k-2},H,V)$.

>>>>

%This section supplies the proofs postponed from Section~\ref{sec:hv:type1}.

We start by presenting two properties underneath the procedures designed in Section~\ref{sec:hv:type1}. These properties will enable us to construct simpler proofs later.

@@

We now proceed to elaborate the proofs postponed from Section~\ref{sec:hv:type1}. The order of the subsequent proofs will not strictly follow the sequence in which they are referenced in Section~\ref{sec:hv:type1}. In particular, we will prove Lemma~\ref{lmm:hv:type1:properties} before Lemma~\ref{lmm:hv:type1:recur-output}, because the claims of the former lemma can be used to produce a succinct argument for the latter.

@@

\extraspacing \underline{\em Proof of Statement (1).} Let $\bm{t}$, $h$, and $v$ be as defined in the statement. 
Recall that $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$. The segments $h$ and $v$ both cross $B_\bm{t}$, as can be verified from the definitions of $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$. Thus, $h \cap v$ is a point in $B_\bm{t} = \bigcap_{i=1}^{k-2} \bm{t}[i]$. As $r_i$ ($i \in [k-2]$) is the full rectangle of $\bm{t}[i]$, we know that $\bigcap_{i=1}^{k-2} r_i$ covers $B_\bm{t} = \bigcap_{i=1}^{k-2} \bm{t}[i]$. Hence, point $h \cap v$ falls in $\bigcap_{i=1}^{k-2} r_i$, indicating that $h\cap v \cap \bigcap_{i = 1}^{k-2}r_i \neq \emptyset$. It follows that $(r_1,...,r_{k-2},h,v)$ is a result tuple in $\J(R_1,...,R_{k-2},H,V)$.
